The globular cluster system of the Auriga simulations

### 2019-12-11 response_to_referee.tex

\begin{document}

\section*{Introduction (of referee report)}
``The results of the paper clearly demonstrate that the technique of simulating
stellar clusters in cosmological hydrodynamical simulations by tagging stellar
particles based on their ages does not reproduce key properties of observed GC 
systems in the Milky Way and M31. However, the authors do not state this conclusion
anywhere''.

We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. Indeed, we do find that age-selected stellar particles do not 
reproduce key properties of observed GC systems in the Milky Way and M31. However,
our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations.

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers, not words.
\item TODO: parenthesis
\item
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

@@

\subsection*{Sect. 3 -}
\begin{itemize}
\item Item 
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item
\item
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item Item
\end{itemize}

\section*{Minor comments}
\begin{itemize}
\item We clarified that `blue' GC subpopulation means metal-poor with [Fe/H]~$<~1$
\item The units of mass-to-light ratio have been corrected.
\item The indicated typos have been corrected.
\item `missing error bars and references for the virial radii' $\rightarrow$
    The reference was given in a footnote, but is now moved to the main text.
\item 4.1: `which model do the authors refer to?' $\rightarrow$ 
    added `star formation'.
\item 4.1: `The top half of the left figure' $\rightarrow$ 
    `The top panel of Figure 3'.
\end{itemize}

### 2019-12-11 AurigaGCS.tex
More fairly straightforward changes

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
biased dark matter (DM) halos at high redshift. Other recent hypotheses of GC formation 
prior to collapse of the proto-galaxy include formation in colliding supershells 
\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift six by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the MW GCS that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $r_{\text{gal}}=\sqrt{(X-r_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $r_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, the two radial distributions are not statistically
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the thirty Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The beige (brown)
        [teal] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Beige triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The purple solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW (separated at
        [Fe/H] = -1 as indicated by the vertical dotted magenta line).
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

% Finally, we test the null hypothesis that MW (M31) and the GC candidates (all,
% {\it in~situ}, and accreted) are drawn from the same underlying distribution 
% by calculating the KS test statistic (i.e. six KS tests per simulation). We 
% reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
% simulations, both for MW and M31, except when comparing the old accreted stars 
% of \mbox{Au4-10} to the MW GCS. In this case we still reject $H_0$ with, but 
% with $\leq 98.68$~\% confidence. When comparing to the M31 GCS, the `best' 
% matches are the old accreted subpopulations of \mbox{Au4-13}, \mbox{Au4-15}, and 
% \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
% and 98.32~\%). Here we find that the cumulative distributions are more or less
% similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
% counts which drives the KS test statistic over the critical values. This affirms
% our finding that the simulations produce GC candidates that are more metal-rich
% than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
% high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
% and over-production of stars with [Fe/H]$\geq$~-0.5.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all thirty Auriga L4 haloes with the 25-75 percentile range 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the beige crosses), but solid (open) dot now
shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
population. We split the radii up into the metal-rich/metal-poor groups by taking
a metallicity cut at [Fe/H]~=~-1 as is done in the literature.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all thirty Auriga
        L4 haloes. Here we consider only the GC candidates and color-code by the 
        median mass (values also shown in each bin). The numbers in parenthesis 
        show how many star particles fall within the bin. Note that the range of 
        the colourmap differs from both panels in Figure~\ref{fig:observations_FeHRgc} 
        (for improved contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}.

>>>>

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
of GC formation prior to collapse of the proto-galaxy include formation in colliding 
supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift $6$ by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the MW GCS that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
$30$~GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $r_{\text{gal}}=\sqrt{(X-r_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $r_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M$_{\odot}$/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, the two radial distributions are not statistically
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the $30$~Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The beige (brown)
        [teal] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Beige triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The purple solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW (separated at
        [Fe/H] = -1 as indicated by the purple dotted vertical line).
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

% Finally, we test the null hypothesis that MW (M31) and the GC candidates (all,
% {\it in~situ}, and accreted) are drawn from the same underlying distribution 
% by calculating the KS test statistic (i.e. $6$ KS tests per simulation). We 
% reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
% simulations, both for MW and M31, except when comparing the old accreted stars 
% of \mbox{Au4-10} to the MW GCS. In this case we still reject $H_0$ with, but 
% with $\leq 98.68$~\% confidence. When comparing to the M31 GCS, the `best' 
% matches are the old accreted subpopulations of \mbox{Au4-13}, \mbox{Au4-15}, and 
% \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
% and 98.32~\%). Here we find that the cumulative distributions are more or less
% similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
% counts which drives the KS test statistic over the critical values. This affirms
% our finding that the simulations produce GC candidates that are more metal-rich
% than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
% high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
% and over-production of stars with [Fe/H]$\geq$~-0.5.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all $30$~Auriga L4 haloes and the 25-75 percentile range 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the $30$~Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the beige crosses), but solid (open) dot now
shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
population. We split the radii up into the metal-rich/metal-poor groups by taking
a metallicity cut at [Fe/H]~=~-1 as is done in the literature.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all $30$~Auriga
        L4 haloes. Here we consider only the GC candidates and color-code by the 
        median mass (values also shown in each bin). The numbers in parenthesis 
        show how many star particles fall within the bin. Note that the range of 
        the colourmap differs from both panels in Figure~\ref{fig:observations_FeHRgc} 
        (for improved contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
$30$~Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}.

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these $25$ bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the bin with metallicities in the range
[Fe/H]~$\in [-2.5, -1.5]$ and gallactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.
